`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`

### 2025-07-09 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/reference-aggregation.Rmd

```{r file paths}
# SingleR results
aggr_singler_file <- file.path(
  results_dir,
  params$sample_id,
  "aggregated",
  glue::glue("{params$library_id}_singler-results.rds")
)

non_aggr_singler_file <- file.path(
  results_dir,
  params$sample_id,
  "not-aggregated",
  glue::glue("{params$library_id}_singler-results.rds")
)

>>>>

```{r file paths}
# SingleR results
aggr_singler_file <- file.path(
  results_dir,
  params$sample_id,
  "aggregated",
  "NE-tumor-combined",
  glue::glue("{params$library_id}_singler-results.rds")
)

non_aggr_singler_file <- file.path(
  results_dir,
  params$sample_id,
  "not-aggregated",
  "NE-tumor-combined",
  glue::glue("{params$library_id}_singler-results.rds")
)
